\begin{acknowledgements}
	
	\vspace{-0.75cm}
	
	{\small %\begin{center}
		%\textit{No man is an island entire of itself, \\
		%	Every man is a piece of the continent,\\
		%	A part of the main.} - John Donne
		%\end{center}
		
		A particularly pernicious myth is that science is moved forward by 
		lone geniuses - this idea is just that, a myth. It would have been 
		impossible for me to get this far without an overwhelming amount of 
		support, a full account of which would likely be as long as the 
		thesis itself. Hopefully, this abbreviated form  will suffice.
		
		Firstly, I would like to thank my supervisors; Ian Dobbie, Martin 
		Booth and Ilan Davis. Their input, feedback, expertise, and 
		encouragement were invaluable to me. Ian in particular was always 
		on hand to offer support and insight at critical moments. I owe 
		everyone I worked alongside at Micron during my time a debt of 
		gratitude, particularly Mick Philips and David Pinto; building and 
		writing code for bespoke super-resolution microscopes has one hell 
		of a learning curve, and you made it much easier for me to climb 
		it. Thank you for showing me the ropes, answering my many questions 
		and for tolerating my more vocal outbursts in the office when 
		Python proved particularly adversarial. 
		
		I received incredible support from the Davis lab, particularly from Richard Parton, Josh Titlow and Dalia Gala in providing biological 
		samples and key feedback. From the Dynamic Optics and Photonics 
		Group, I am extremely grateful to Mantas \v{Z}urauskas, Jacopo 
		Antonello and Syed Hussain for their expertise and advice on 
		adaptive optics. It has been my immense pleasure to learn from and 
		work alongside such accomplished individuals. 
		
		My thanks to Sara Abrahamsson and Marcel M\"{u}ller for their encouragement and willingness to collaborate with me on a number of occasions. 
		
		The 2016 ONBI cohort, program coordinator Peter Jezzard, and 
		administrator Lisa Bligh all deserve thanks for building a 
		supportive environment to enjoy camaraderie, laughter, and many, 
		many caterpillar cakes.
		
		Rick Lange, Sarah Fynes-Clinton, Barney Bridges, Leah Barton, 
		John-Luke Treadgold, Simon Parnham, Jon Collins, Tim Curtis, and 
		Kyle Hall have all given me unflagging support, encouragement, and 
		enthusiasm. They have been boundless sources of joy, levity, and 
		steadfast bulwarks when I needed them most. I will never forget 
		their faultless kindness to me. If a man's wealth is indeed 
		measured by his friendships, I am rich beyond all measure.
		
		Finally, I would like to thank my family: my parents, Trevor and 
		Karen Hall; my sister and brother-in-law, Annabelle and Christopher 
		Holloway; and my sister, Meghan Hall. They have consistently been 
		my most vocal supporters, and fierce sources of love and 
		encouragement. The fruits of my labour are a testament to the good
		soil I was planted in and the nourishment I received from them.
		
		You all have my eternal gratitude and my most heartfelt, effusive 
		thanks.}
	
\end{acknowledgements}